Multiple imputation of incomplete multilevel data using Heckman selection models

### 2022-10-31 1.Paper/Paper.Rmd
Update figures

```{r rhosize,fig.pos="h",fig.cap="\\label{fig:size} Comparison of methods for continuous incomplete variable under systematical missingness by varing (N=number of clusters- $n_i$=sample size per cluster), the dashed line depicts the true simulated parameter value",echo=FALSE,fig.keep="last"}
plot_N
```

>>>>

```{r rhosize,fig.pos="h",fig.cap="\\label{fig:size} Comparison of methods for continuous incomplete variable under systematical missingness by varing (N=number of clusters;$n_i$=sample size per cluster), the dashed line depicts the true simulated parameter value",echo=FALSE,fig.keep="last"}
plot_N
```
